Adapting the Chumbley Score to Bullet Striations

### 2018-04-25 presentation/presentation.Rmd
some other presentation changes
pres changes

### Structure
- Data being used
- What is the Chumbley Score Method?
- Identifying Best parameter Settings for Bullets
- Modifications to the Algorithm
- Results using \citet{hadler} method and results using Modified method

>>>>

### Structure
- Error rates in toolmarks
- Data being used
- What is the Chumbley Score Method?
- Identifying Best parameter Settings for Bullets
- Modifications to the Algorithm
- Results
